Motional Ground-State Cooling Outside the Lamb-Dicke Regime

### 2017-07-09 paper.tex
Anharmonicity number

Two additional challenges of cooling single sodium atoms are
further identified and addressed experimentally.
First, the high initial temperature causes population in high motional states
means that the atoms sample anharmonicity of the trap away from the center.
In order to address trap anharmonicity, we drive sidebands with a large Rabi frequency
and short pulses to Fourier broaden spectrum coverage.
For the higher trap frequency radial directions, anharmonicity is calculated to be 1kHz/n,
Rabi frequency exceeds tens of kHz is needed to couple to \fxnote{??\%} population up to
\fxnote{n=?(we should calculate this)}.
Second, the  tweezer trap  causes a large AC Stark shift (as large as $300$ MHz)
in the excited state. This creates  a large, position-dependent OP detuning
and mixes the excited-state hyperfine levels, and therefore reduces the optical pumping fidelity.
We solve this issue by switching the trapping light at 3 MHz during the whole cooling sequence,
similar to our loading and imaging process~\cite{Hutzler2017-LightShifts},
while leaving OP on with constant intensity.
Due to the large light shift, the optical pumping is effectively off when the trap light is on.
Since the atom can only be addressed by the optical pumping light when the trap light is off,
the effect of light shift on optical pumping fidelity is suppressed.

>>>>

Two additional challenges of cooling single sodium atoms are
further identified and addressed experimentally.
First, the high initial temperature causes population in high motional states
means that the atoms sample anharmonicity of the trap away from the center.
In order to address trap anharmonicity, we drive sidebands with a large Rabi frequency
and short pulses to Fourier broaden spectrum coverage.
For the higher trap frequency radial directions, anharmonicity is calculated to be 1kHz/n,
Rabi frequency of at least $15$ kHz is needed to couple to $99$\% population up to $n=15$.
Second, the  tweezer trap  causes a large AC Stark shift (as large as $300$ MHz)
in the excited state. This creates  a large, position-dependent OP detuning
and mixes the excited-state hyperfine levels, and therefore reduces the optical pumping fidelity.
We solve this issue by switching the trapping light at 3 MHz during the whole cooling sequence,
similar to our loading and imaging process~\cite{Hutzler2017-LightShifts},
while leaving OP on with constant intensity.
Due to the large light shift, the optical pumping is effectively off when the trap light is on.
Since the atom can only be addressed by the optical pumping light when the trap light is off,
the effect of light shift on optical pumping fidelity is suppressed.
